Contracts for Contracts

### 2023-07-12 paper/introduction.tex
some typo

To prevent such attacks, the programmer needs to specify those critical
conditions. The execution is allowed only when those conditions are met.
However, we observe that existing popular smart contract languages (e.g.,
Solidity) do not provide \emph{expressive, effective, convenient} means to
\emph{specify} and \emph{enforce} contract behaviors.
Simple first-order assertion primitives are indeed available, but they cannot
effectively examine callable addresses or function values,
%\zz{are function values referring to high-order functions?}
which exhibit
higher-order behaviors and are a common pattern used in developing smart contract
programs.
%Moreover, many of the critical conditions in smart contracts are \emph{temporal}
%-- the order of events matters.
%For instance, to defense the DAO attack caused by reentrancy via
%external functions, it requires to check that the function of interest cannot
%be invoked \emph{before} the current call of the same function is finished.
The lack of sufficient linguistic means to specify and enforce subtle but
critical behaviors discourages programmers to write clean and maintainable
code with higher-level abstractions.
Instead, programmers are obliged to write verbose low-level code
to implement security checks, which conflates the main business logic with
behavioral checks, further leading to poor readability and maintainability.
%The pervasive temporal conditions in distributed blockchain systems further
%complicates the situation: these temporal behavioral checks are usually
%encoded as value-level checks in ad-hoc manners.
%Taking the DAO attack as example again, a common way to implement ``reentrancy
%guards'' is to manually define an additional boolean flag, indicating
%whether the function is finished. This is both verbose and error-prone,
%quickly becoming unmanageable for complex behaviors.
And often worse, defensive checks are forgotten or disregarded, leading to
vulnerable code causing real monetary lose.

@@

In this paper, we develop the first behavioral contract system \lang (Contract
Solidity) for the Solidity language, providing a practical specification and
monitoring system for both first-order and higher-order behaviors.
%monitoring system for both \emph{higher-order and temporal behaviors}.
Solidity is a programming language to build smart contract programs that run on
the Ethereum platform.  As one of the most popular ecosystem of smart
contracts, Solidity has been used \todo{to do cool things}.
\todo{explain challenges}

@@

One type of values in Solidity that exhibits higher-order behaviors is \emph{addresses}.

@@

Compared to existing approaches \todo{of what}, our work is both expressive,
easy-to-use, lightweight, effective, and economical.
Programmer can use all Solidity expressions to define the desired property,
which are attached only to relevant functions in a non-intrusive way.

>>>>

To prevent such attacks, the programmer needs to specify those critical
conditions. The execution is allowed only when those conditions are met.
However, we observe that existing popular smart contract languages (e.g.,
Solidity) do not provide \emph{expressive, effective, convenient} means to
\emph{specify} and \emph{enforce} contract behaviors.
Simple first-order assertion primitives are indeed available, but they cannot
effectively examine callable addresses or function values,
%\zz{are function values referring to high-order functions?}
which exhibit
higher-order behaviors and are a common pattern used in developing smart contract
programs.
%Moreover, many of the critical conditions in smart contracts are \emph{temporal}
%-- the order of events matters.
%For instance, to defense the DAO attack caused by reentrancy via
%external functions, it requires to check that the function of interest cannot
%be invoked \emph{before} the current call of the same function is finished.
The lack of sufficient linguistic means to specify and enforce subtle but
critical behaviors discourages programmers to write clean and maintainable
code with higher-level abstractions.
Instead, programmers are obliged to write verbose low-level code
to implement security checks, which conflates the main business logic with
behavioral checks, further leading to poor readability and maintainability.
%The pervasive temporal conditions in distributed blockchain systems further
%complicates the situation: these temporal behavioral checks are usually
%encoded as value-level checks in ad-hoc manners.
%Taking the DAO attack as example again, a common way to implement ``reentrancy
%guards'' is to manually define an additional boolean flag, indicating
%whether the function is finished. This is both verbose and error-prone,
%quickly becoming unmanageable for complex behaviors.
And often worse, defensive checks are forgotten or disregarded, leading to
vulnerable code causing real monetary loss.
\todo{need a concrete motivating example?}

@@

In this paper, we develop the first behavioral contract system \lang (Contract
Solidity) for the Solidity language, providing a practical specification and
monitoring system for both first-order and higher-order behaviors.
%monitoring system for both \emph{higher-order and temporal behaviors}.
Solidity is a programming language to build smart contract programs that run on
the Ethereum platform.  As one of the most popular ecosystems of smart
contracts, Solidity has been used \todo{to do cool things}.
\todo{explain challenges}

@@

One type of value in Solidity that exhibits higher-order behaviors is \emph{addresses}.

@@

Compared to existing approaches \todo{of what}, our work is both expressive,
easy-to-use, lightweight, effective, and economical.
Programmers can use all Solidity expressions to define the desired property,
which are attached only to relevant functions in a non-intrusive way.
